---
title: "Shiny Presentation"
author: "Mat Dac"
date: "December 29, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(MASS)
```

## Introduction

The inteactive shiny application is running at <https://matdacnev.shinyapps.io/shinyAssignment/>.

When the user clicks on the check box, the app will fit either an OLS or a robust regression to the Iris data points shown in the plot.

The robust regression is less sensitive to outliers and is preferred if the data are non-normal.

## Coefficients

The 2 regressions are fitted on the server side of the shiny app:

```{r fit, echo = TRUE}
X = iris$Sepal.Width; Y = iris$Petal.Width
lm.fit = lm(Y ~ X, data=iris)
rlm.fit = rlm(Y ~ X, data=iris)
```

The coefficients for the OLS and robust regressions are the following:

```{r coef, echo = TRUE}
coef(lm.fit)
coef(rlm.fit)
```

## Plot

In this slide, the 2 regression lines are shown. But in the shiny app, the user can choose which line to show.

```{r plot, echo = TRUE}
plot(X, Y, col=iris$Species, xlab="Sepal Width", ylab="Petal Width", main="Iris Data")
abline(lm.fit, lty=1)
abline(rlm.fit, lty=2)
legend("topright", c("OLS", "Robust"), lty=c(1, 2))
```

## Conclusion

Shiny applications are great to interact with data.


